Restructuring Data for Exascale Scientific Productivity

### 2016-03-02 papers/2016-Supercomputing/paper.tex
added notes from the PLAN.JPEG picture from our in person paper plans

Be sure to address the following:\\
1. Why should Chang or Chen care from the apps side.\\
2.why should ken or hank care from the viz side\\
3.why would Garth care from the storage side\\

@@

>>>>

Be sure to address the following:\\
1. Why should Chang or Chen care from the apps side.\\
2. why should ken or hank care from the viz side\\
3. why would Garth care from the storage side\\

@@

Contributions:\\
\begin{enumerate}
\item XGC1 Byte-split data (3/5)
\begin{enumerate}
\item decomposition/compression
\item auditor
\item data challenges preventing arbitrary use
\end{enumerate}
\item XGC1/S3D Data Interpolation (timestep to timestep)
\end{enumerate}

Engineering:\\
\begin{enumerate}
\item ADIOS write transports
\item VisIt auditor reader
\item interfaces
\end{enumerate}

validation/experiments (XGC1 only for now, 1 & 2 buckets, all other factors):\\
\begin{enumerate}
\item Performance writing (A orig, B 2 buckets)
\item Performance reading (A orig, B 2 buckets, C bucket 1, D, bucket 2)
\item Visualization diff (3-d)
\item numeric evaluation diff (to get past criticism of 3-d hiding errors)
\item derived quantity
\item interpolation validation
\end{enumerate}

target: Lustre, DataSpaces\\
nodes: 10, 100, 1000 (Sith 35 compute + 5 storage)\\
data/node: 10M, 1G\\
vars: 10, 100\\
per var: 1, 2 buckets (4 if we have time)\\
timesteps: 2, 4, 8, 16\\
time between timesteps: 10s, 100s\\

XGC1:\\
1d array format\\
nparticles (N x 8)\\
fields (nv) (3-5 vars)\\

Pixie3D/S3D:\\
3d array: (1k x 1k x 1k)\\

Use ITER mesh input for XGC1

Viz diff

\{reduced, full, diff\} images, numerical eval of diff\\

Responsibilities:
\begin{itemize}
\item Jay - write draft/drive paper
\item everyone - experiment runs
\item Ivan - DataSpaces help
\item Tahsin/Jong - Use real XGC1 data in test harness
\item Tahsin/Jong - Big run for byte split example
\item Tahsin/Jong - small run for interpolation example
\item Hadan - Real S3D run
\item Hasan/Norbert - ADIOS writer
\item James/Dave - ADIOS reader/viz
\item Hasan/Ben - ADIOS interpolation pieces
\end{itemize}
